Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
add satellite applications

\red{[All very interesting, however we never start from a $G(s)$ plant, we never really display the whole capabilities of the technique! Or am I missing something?]}

@@

>>>>

@@

A third set of benchmarks that consists of digital controllers for satellite applications
is considered~\cite{Franklin15}, in order to evaluate the present approach full capabilities.
In particular, satellites often require attitude (pose) control for proper orientation 
of antennas and sensors w.r.t. earth. The satellite attitude control is typically used 
for three-axis attitude tracking, but here only one axis at a time is considered. 
The motion equation for the one-axis system, despising disturbance torques, is given by:
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C},
\end{equation}

\noindent where $I$ is the inertia moment of satellite about its mass center, $\tau_{C}$ is the control 
torque applied by thusters, and $\theta$ is the controlled attitude angle. 
Normalizing Eq.~\eqref{eq:satelliteode} by defining the control signal $u=\frac{\tau_{C}}{I}$ and 
taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained:
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}

\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, the following $z$-domain model is obtained:
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}.
\end{equation}
